Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline

### 2014-02-11 paper.tex
Unsure what happened in this edit

Figure~\ref{fig:CPE_Scaling} shows measured data and the corresponding fits for both the CPE magnitude at 0.05\thinspace Hz and $R_{S+bulk}$. The resulting model parameters $m$, $k$, and $|Z|\thinspace @\thinspace 1Hz$ are shown in table~\ref{tab:CPEparams}. Here we express the CPE offset parameter as $|Z|\thinspace @ \thinspace 1Hz$, but the fits used $|Z|\thinspace @ \thinspace 0.05Hz$, as data points at this frequency are outside the transitional zone where the impedance of the CPE and that of $R_{S+bulk}$ overlap.
{
    \color{blue} The data presented in Fig.~\ref{fig:CPE_Magnitude} show a large, linear, relative shift of $|Z|$ with salinity at higher frequencies, where the resistive component of the solution dominates.
Conversely, at lower frequencies where the $|Z|$ changes with frequency, the relative change is closer to logarithmic. This region is modeled by the CPE. 
}
This suggests that the CPE does not rely on the added ions but they do have an effect, implying that its behaviour is a property of platinum and $H_{2}O$.

@@

\section{Faradaic Parameters}
{
    \color{blue}
    Our model uses two reverse connected diodes to represent Faradaic current conduction between electrode and electrolyte. Specifically we use the diodes to model irreversible Faradaic reactions. Any reversible reactions, those producing reactants bound to the surface of the electrode, are encapsulated by the displacement branch (CPE) of the model.
    Possible irreversible Faradaic reactions for platinum electrodes in saline are:
    \begin{eqnarray}
        Pt + 4Cl^{-} &\Rightarrow& [PtCl_{4}]^{2-} + 2 e^{-}\\
        2H_{2}O + 2 e^{-} &\Rightarrow& H_{2}\uparrow + 2OH^{-}\\
        2H_{2}O &\Rightarrow& O_{2}\uparrow + 4H^{+} + 4e^{-}\\
        2Cl^{-} &\Rightarrow& Cl_{2}\uparrow + 2e^{-}\\
        Cl^{-} + H_{2}O &\Rightarrow& ClO^{-} + 2H^{+} + 2e^{-}
    \end{eqnarray} 
}
With parameters fitted for the scaling of both the CPE and $R_{S}$ with PBS concentration, we evaluate Faradaic conduction. The interface model uses two reverse connected diodes to reproduce the exponential behaviour of Faradaic current conduction, implied by the Butler-Volmer equation. We wish to measure this conduction by separating it from the displacement behaviour of the CPE. By using a DC measurement technique, as opposed to cyclic measurements, we are able to separate the effects in time. 
Like a conventional capacitor, when the voltage across the CPE changes, it responds by absorbing or ejecting charge, causing a spike in current. The CPE will draw negligible current once it has settled and in the case of our model we assume the remaining current conduction to be the result of Faradaic processes. 
{\color{blue} In \cite{Greatbatch1969} it is shown that the stirring of an air-saturated solution of physiological saline reduces the settling time of platinum electrodes to stimulus transients; with both situations eventually settling to the same impedance.}
The equation governing current conduction in a diode where the forward voltage across the diode, $V_{D}$, is small is
\begin{equation}
    I = i_{0}  e^{V_{D} / n V_{T}}
\end{equation}
where $V_{T}$ is the thermal voltage and is approximately 25\thinspace mV at a temperature of 300\thinspace K. We wish to find how the saturation current ($i_{0}$) and the ideality factor ($n$) scale as the solution salinity is varied.

Faradaic measurements were made using an Agilent E5270B Precision Measurement Mainframe producing a stepped DC voltage stimulus across electrodes 3 and 7 whilst continuously measuring the output current. 
{
    \color{blue}
    The use of electrodes 3 and 7 was made because the connection to electrode 2 in our Octrode had been damaged. This alteration has no impact on the validity of results as all other electrodes are left to float.
}

Measurements commenced with a 4.5 litre solution of 1.0X PBS which was progressively diluted in factors of two between each measurement. The solution was mixed continuously using a standard laboratory grade magnetic stirrer. The solution was in equilibrium with air prior to and during measurement and the electrodes remained submerged at all times.
A single measurement run involved stepping the voltage across electrodes 2 and 7 from 0.5\thinspace V to 1.2\thinspace V in increments of 0.05\thinspace V; this range was previously determined to capture the onset of Faradaic conduction.

@@

{
    \color{blue}
    Figure~\ref{fig:faradaic_currentVsTime} shows a subset of the data used in Fig.~\ref{fig:StepResponse_Faradaic} (the 1.0X PBS trace) to show the fit between simulated and measured data in the time domain. Here the simulation contains fitted diode parameters, shown in table~\ref{tab:FaradaicParams}, which give rise to the exponentially increasing steady state current.     
It is apparent from this trace that the temporal response of the CPE does not match the transient decay curves seen in the Faradaic measurements, something the CPE should predict. These transient decay curves appear to have time-constant that decreases with each subsequent measurement. This variable time-constant phenomena is especially clear when looking back at figure~\ref{fig:CPE_currentVsTime}. Although the Faradaic response transients appear to approach the time-constant predicted by the CPE, there is still behaviour not completely described by the CPE. 
The match between fitted diode parameters ($n$ and $i_{0}$) and the measurement data 64 seconds after each voltage increment has been plotted in figure~\ref{fig:faradaic_currentVsVoltage}. This graph plots current conducted at 64 seconds after each step in terms of voltage applied across electrodes 3 and 7.

In future we hope to extend this model into a diffusion controlled conduction scenario and extend the CPE element to better reproduce the time domain response, which we hope to publish in a follow-up paper.
}
\section{In-vivo measurements of sheep}

@@

We now test the claim that 0.1X PBS is a reasonable representation of the spine of a living sheep.
The displacement measurements were repeated inside the spinal canal of a live sheep, just outside the dura as shown in figure~\ref{fig:sheepSpine}. The sheep were prepared and anaesthetised using the procedures described in \cite{Parker2013} under the Animal Care and Ethics Committee approval of the Royal North Shore Hospital. The study complied with the Australian Code of Practice for the Care and Use of Animals for Scientific Purposes.
{\color{blue} Four measurements taken at regular invervals over a period of 30 minutes} are presented in figures~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase} on top of the array of traces for saline taken from figures~\ref{fig:CPE_Magnitude} and~\ref{fig:CPE_Phase}.
Although it is clear that there are complications in vivo, a 0.25X PBS saline offers a good approximation to the resistive part of the trace.
The reactive part would be better modelled by a solution of less than 0.025X concentration.

@@

5. The previous point is complicated by your statement that Rs (Fig 2) is an addition to the volume resistance (p2 RH col). Why is Rs necessary? Is it because the resistance values at high frequencies in Fig 4 are not consistent with the values from the resistor network found in section II? If so, this would be very interesting and I would like you to bring this out.\\
{\color{OliveGreen} 
    Item 24\\
    {\color{Red} His reasoning is correct, it is because the impedance does not match at high freq. I had the graph with dotted lines to show the difference that Rs made. Jonathan, you thought this was too messy and it was removed, should it be added back in again?}
    No response yet.
}\\

6. P2, col 2, line 24: why 2 \& 7?\\
{\color{OliveGreen}
    Item 25\\
    {\color{Red} Explain more clearly why electrodes 2 and 7 were chosen (to avoid end effects)}
    No response yet.
}\\

@@

14. P5, col 1, line 49 ``a 0.25X PBS is a good model''.  This seems a very feeble comment on an interesting result. The series resistance part of the in vivo magnitude is a good fit to the 0.25X curve and the slope of the CPS is very similar (though you have exaggerated this by extrapolating nearly 2 decades in frequency below the lowest-frequency measurement). But the impedance at low frequencies is about three times too high. How do you explain that? It cannot be because of the bone and other high-resistivity structures around the electrodes (which would have an effect on the high frequency asymptote). So what is it? Did you measure the electrodes again in PBS after removing from the sheep? Troyk published an interesting paper with measurement from electrodes in brain of zebra finches which showed that anomalous characteristics in vivo vanished as soon as the electrodes were returned to PBS, implying that the phenomenon was not due to some biofilm deposited on the electrodes.\\
{\color{OliveGreen}
    Item 33\\
    {\color{Red} True, a feeble comment on PBS match. It may be worth noting the phase of measured data in sheep indicating that the sheep itself was reactive. There may be data at those lower points (to justify extrapolating), check. Have we measured the electrodes again since inserting into the sheep, I think we have but check.  Read the paper by Troyk, comment on applicability. Maybe there is test data between sheep in saline showing the electrodes returning to normal, check.}.
    No response yet.
}\\
}

@@

Overall, the paper was brief and to the point, which in this case is actually a determent instead of a benefit. Much of the underlying theory and development of parameters appear without informing the reader of their purpose or how they were calculated and/or measured. 
For example, the parameters in Table 2 (and reported to be in Figure 3) are not explained and what their relationship to the remainder of the manuscript is not provided. 
{\color{OliveGreen}
    Item 34\\
    {\color{Red} Explain parameters in table two better or refer readers to ScottSingle2013}
    No response yet.
}
To make this manuscript more approachable to a wider audience, I recommend the authors more fully develop Sections II, III, and IV. Further, they should explain their testing in terms of standard electrochemical characterization, detailing their counter, working, and reference electrodes used in measuring impedance. 
{\color{OliveGreen}
    Item 35\\
    {\color{Red} Try to include any relevant electrochemical information, find out what that is first}
    No response yet.
}
As part of this expansion, the references should be increased beyond the present ten references. Although their current references include clearly important electrode characterization references (Cogan, Merrill et. al, \& Kane et. al), the information contained in these references are not effectively used to support the authors’ work.\\
{\color{OliveGreen}
    Item 36\\
    {\color{Red} Perhaps Troyk could be added. References have been extended to include a Masters Theses and Neuroprosthetics: Theory and practise book}
}

>>>>

Figure~\ref{fig:CPE_Scaling} shows measured data and the corresponding fits for both the CPE magnitude at 0.05\thinspace Hz and $R_{S+bulk}$. The model parameters $m$, $k$, $|Z|\thinspace @\thinspace 1Hz$, and $R_S$ are shown in table~\ref{tab:CPEparams}, with $|Z|\thinspace @\thinspace 1Hz$, and $R_S$ given as functions of concentration. 
Here we express the CPE offset parameter as $|Z|\thinspace @ \thinspace 1Hz$, but the fits used $|Z|\thinspace @ \thinspace 0.05Hz$, as data points at this frequency are outside the transitional zone where the impedance of the CPE and that of $R_{S+bulk}$ overlap.
{
    \color{blue} The data presented in Fig.~\ref{fig:CPE_Magnitude} show a large, linear, relative shift of $|Z|$ with salinity at higher frequencies, where the resistive component of the solution dominates.
Conversely, at lower frequencies where the $|Z|$ changes with frequency, the relative change is closer to logarithmic. This region is modeled by the CPE. 
This suggests that the CPE does not chiefly rely on the added salt ions, but they do have some effect. 
Instead, the constant-phase charge effect must arise from phenonema not associated with the salt ions.
}

@@

\section{Faradaic Parameters}

With parameters fitted for the scaling of both the CPE and $R_{S}$ with PBS concentration, we turn to Faradaic conduction. 
{
    \color{blue}
    Our model uses two reverse connected diodes to represent Faradaic current conduction between electrode and electrolyte. Specifically we use the diodes to model irreversible Faradaic reactions. (Any reversible reactions, those producing reactants bound to the surface of the electrode, are encapsulated by the displacement branch (CPE) of the model.)
    Possible irreversible Faradaic reactions for platinum electrodes in saline are:
    \begin{eqnarray}
        Pt + 4Cl^{-} &\Rightarrow& [PtCl_{4}]^{2-} + 2 e^{-}\\
        2H_{2}O + 2 e^{-} &\Rightarrow& H_{2}\uparrow + 2OH^{-}\\
        2H_{2}O &\Rightarrow& O_{2}\uparrow + 4H^{+} + 4e^{-}\\
        2Cl^{-} &\Rightarrow& Cl_{2}\uparrow + 2e^{-}\\
        Cl^{-} + H_{2}O &\Rightarrow& ClO^{-} + 2H^{+} + 2e^{-}
    \end{eqnarray} 
}
The interface model uses the diodes to reproduce the exponential behaviour of Faradaic current conduction implied by the Butler-Volmer equation. We wish to measure this conduction by separating it from the displacement behaviour of the CPE. By using a DC measurement technique, as opposed to cyclic measurements, we are able to separate the effects in time. 
Like a conventional capacitor, when the voltage across the CPE changes, it responds by absorbing or ejecting charge, causing a spike in current. The CPE will draw negligible current once it has settled and in the case of our model we assume the remaining current conduction to be the result of Faradaic processes. 
{\color{blue} In \cite{Greatbatch1969} it is shown that the stirring of an air-saturated solution of physiological saline reduces the settling time of platinum electrodes to stimulus transients; with both situations eventually settling to the same impedance.}
The equation governing current conduction in a diode where the forward voltage across the diode, $V_{D}$, is small is
\begin{equation}
    I = i_{0}  e^{V_{D} / n V_{T}}
\end{equation}
where $V_{T}$ is the thermal voltage and is approximately 25\thinspace mV at a temperature of 300\thinspace K. We wish to find how the saturation current ($i_{0}$) and the ideality factor ($n$) scale as the solution salinity is varied.

Faradaic measurements were made using an Agilent E5270B Precision Measurement Mainframe producing a stepped DC voltage stimulus whilst continuously measuring the output current. 
%{
%    \color{blue}
%    The use of electrodes 3 and 7 was made because the connection to electrode 2 in our Octrode had been damaged. This alteration has no impact on the validity of results as all other electrodes are left to float.
%}

Measurements commenced with a 4.5 litre solution of 1.0X PBS which was progressively diluted in factors of two between each measurement. The solution was mixed continuously using a standard laboratory grade magnetic stirrer. The solution was in equilibrium with air prior to and during measurement and the electrodes remained submerged at all times.
A single measurement run involved stepping the voltage across the electrodes from 0.5\thinspace V to 1.2\thinspace V in increments of 0.05\thinspace V; this range was previously determined to capture the onset of Faradaic conduction.

@@

{
    \color{blue}
    Figure~\ref{fig:faradaic_currentVsTime} shows a subset of the data used in Fig.~\ref{fig:StepResponse_Faradaic} (the 1.0X PBS trace) to show the fit between simulated and measured data in the time domain. Here the simulation contains fitted diode parameters, shown in table~\ref{tab:FaradaicParams}, which give rise to the exponentially increasing steady state current.     
It is apparent from this trace that the temporal response of the CPE does not match the transient decay curves seen in the Faradaic measurements, something the CPE should predict. These transient decay curves appear to have time-constant that decreases with each subsequent measurement. This variable time-constant phenomena is especially clear when looking back at figure~\ref{fig:CPE_currentVsTime}. Although the Faradaic response transients appear to approach the time-constant predicted by the CPE, there is still behaviour not completely described by the CPE. 
The match between fitted diode parameters ($n$ and $i_{0}$) and the measurement data 64 seconds after each voltage increment has been plotted in figure~\ref{fig:faradaic_currentVsVoltage}.

In future we hope to extend this model into a diffusion controlled conduction scenario and extend the CPE element to better reproduce the time domain response.
}
\section{In-vivo measurements of sheep}

@@

We now test the claim that 0.1X PBS is a reasonable representation of the spine of a living sheep.
The displacement measurements were repeated inside the spinal canal of a live sheep, just outside the dura as shown in figure~\ref{fig:sheepSpine}. The sheep were prepared and anaesthetised using the procedures described in \cite{Parker2013} under the Animal Care and Ethics Committee approval of the Royal North Shore Hospital, Sydney. The study complied with the Australian Code of Practice for the Care and Use of Animals for Scientific Purposes.
{\color{blue} Four measurements taken at regular invervals over a period of 30 minutes} are presented in figures~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase} on top of the array of traces for saline taken from figures~\ref{fig:CPE_Magnitude} and~\ref{fig:CPE_Phase}.
Although it is clear that there are complications in vivo, a 0.25X PBS saline offers a good approximation to the resistive part of the trace.
The reactive part would be better modelled by a solution of less than 0.025X concentration.

@@

5. The previous point is complicated by your statement that Rs (Fig 2) is an addition to the volume resistance (p2 RH col). Why is Rs necessary? Is it because the resistance values at high frequencies in Fig 4 are not consistent with the values from the resistor network found in section II? If so, this would be very interesting and I would like you to bring this out.\\
{\color{OliveGreen} 
    Item 24\\
    {\color{Red} His reasoning is correct, it is because the impedance does not match at high freq. I had the graph with dotted lines to show the difference that Rs made. Jonathan, you thought this was too messy and it was removed, should it be added back in again?}
% No sadly not interesting just related to the fact that interface has its own internal resitance.
    No response yet.
}\\

6. P2, col 2, line 24: why 2 \& 7?\\
{\color{OliveGreen}
    Item 25\\
% Because consistent with prev pub plus it doesnt matter which STRESS THIS.
    {\color{Red} Explain more clearly why electrodes 2 and 7 were chosen (to avoid end effects)}
    No response yet.
}\\

@@

14. P5, col 1, line 49 ``a 0.25X PBS is a good model''.  This seems a very feeble comment on an interesting result. The series resistance part of the in vivo magnitude is a good fit to the 0.25X curve and the slope of the CPS is very similar (though you have exaggerated this by extrapolating nearly 2 decades in frequency below the lowest-frequency measurement). But the impedance at low frequencies is about three times too high. How do you explain that? It cannot be because of the bone and other high-resistivity structures around the electrodes (which would have an effect on the high frequency asymptote). So what is it? Did you measure the electrodes again in PBS after removing from the sheep? Troyk published an interesting paper with measurement from electrodes in brain of zebra finches which showed that anomalous characteristics in vivo vanished as soon as the electrodes were returned to PBS, implying that the phenomenon was not due to some biofilm deposited on the electrodes.\\
{\color{OliveGreen}
    Item 33\\
% We can dial up shift in cpe and bulk resistance to create a better match using available chemical reagenre. we hope to synth a superior phantom through combos of saline solvets and hydrolysed cellulose. we anticipate crateing a superios phantom using. one of the goals of one of our industrial partners.
    {\color{Red} True, a feeble comment on PBS match. It may be worth noting the phase of measured data in sheep indicating that the sheep itself was reactive. There may be data at those lower points (to justify extrapolating), check. Have we measured the electrodes again since inserting into the sheep, I think we have but check.  Read the paper by Troyk, comment on applicability. Maybe there is test data between sheep in saline showing the electrodes returning to normal, check.}.
    No response yet.
}\\
}

@@

Overall, the paper was brief and to the point, which in this case is actually a determent instead of a benefit. Much of the underlying theory and development of parameters appear without informing the reader of their purpose or how they were calculated and/or measured. 
For example, the parameters in Table 2 (and reported to be in Figure 3) are not explained and what their relationship to the remainder of the manuscript is not provided.

{\color{OliveGreen}
    Item 34\\
    {\color{Red} Explain parameters in table two better or refer readers to ScottSingle2013}
    We have expanded the explanation in the manuscript, and referred interested readers to the source.
}
To make this manuscript more approachable to a wider audience, I recommend the authors more fully develop Sections II, III, and IV. Further, they should explain their testing in terms of standard electrochemical characterization, detailing their counter, working, and reference electrodes used in measuring impedance. 
{\color{OliveGreen}
    Item 35\\
% No reference elect possible in an implated scenario. Much of problem stems fro trad. electchem are inepplicable or impodssible. much or ou rreviewers arises fro fact that we are operating ni  an scenario far fro trad electrochem labs.
    {\color{Red} Try to include any relevant electrochemical information, find out what that is first}
    No response yet.
}
As part of this expansion, the references should be increased beyond the present ten references. Although their current references include clearly important electrode characterization references (Cogan, Merrill et. al, \& Kane et. al), the information contained in these references are not effectively used to support the authors’ work.\\
{\color{OliveGreen}
    Item 36\\
% In response to numersios reviewese commnets we have added citations we hope we have more thoroughly put more thoro pointers to the literature in  nour manuscript...  After extensice ... we have added citations
    {\color{Red} Perhaps Troyk could be added. References have been extended to include a Masters Theses and Neuroprosthetics: Theory and practise book}
}
